---
title: "HW11: Question 3"
author: "Jamie Ash"
date: "2022-10-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rje)
```

To answer this question I felt like I needed an equation that describes how each
natural number is produced. I began by handwriting out by calculating the 1 
through 10 of $\in N$ to see if there was a pattern. I realized that the even 
numbers where reproduced by summing all possible combinations of $2^n$

for $\{ \mathbb{N}:2^n \}$ which looks like $\{2, 4, 8, 16...\}$ I realized you 
can get all even numbers between $n$ and $n+1$ by raising all possible subsets of 
$1$ to $n$ by two and summing them the individual subsets. Then the odd numbers 
can be found by adding $2^0$ to the set of even numbers, and since $2^0$ is not
in the set $\{ \mathbb{N}:2^n \}$ it does not break the rules of the question.  

```{r}
raise = function(x){
  sum(2^x) 
  }

# first few natural numbers
n = 1:2
# produce the power set of n
sets = powerSet(n, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
evens = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
evens = unlist(evens)
sort(evens)

# retrieveing all odd numbers
sort(evens + 2^0)
```
0 and 1 being the empty set sum of the empty set and the sum of the empty set 
plus $2^0$.

I then realized that $\mathbb{N}$ can be found by individualy summing the subsets 
within the power set of $\{n \in \mathbb{N}:2^n \}$ and also including 0. This is 
the same as adding $2^0$ to $\{n \in \mathbb{N}:2^n \}$

```{r}
# first few positive integers
z = 0:3
# produce the power set of z
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of z (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
Finally, if I go into the negative and sum the first few smallest (and largest 
negative) values in $\mathbb{Z}$, this would be like adding fractions to the 
set of $\{n \in \mathbb{N}:2^n \}$. Like $\{z \in \mathbb{Z}:2^z \}$. I realized
I start getting the set of real numbers, $\mathbb{R}$. 

```{r}
# first few natural numbers
z = -1:1
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
As we go more negative we achieve a higher "resolution". It seems like for each 
integer into the negative we go, one more decimal place is retrieved. For
$z \in Z$ where $-2 \le z \le1$ we get...

```{r}
# first few natural numbers
z = -2:1
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```

adding one more negative integer, $-3 \le z \le1$ we get...
```{r}
# first few natural numbers
z = -3:1
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
So then, is $\mathbb{R^+}$ the individual sums of the subsets of $P(\mathbb{Z})$ 
raised by 2? This also makes me think that $\mathbb{R^+}$ can be achieved 
by individualy summing the subsets in the power set of rational numbers. I did
not complete a proof for power sets. If all this is true maybe it could be a fun
way to get credit for writing a proof with power sets. Infinity gets involved 
though so maybe it is just false. 

Anyway, this is not what the question asked, but I spent too long thinking 
about it, so I have copied an answer from the internet for the sake of time. 



























