---
title: "HW11: Question 3"
author: "Jamie Ash"
date: "2022-10-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rje)
```

To answer this question I felt like I needed an equation that describes how each
natural number is produced. I began by handwriting out the calculation for the 1 
through 10 of $\in N$ to see if there was a pattern. I realized that the even 
numbers where reproduced by summing all possible combinations of $2^n$

for $\{ \mathbb{N}:2^n \}$ which looks like $\{2, 4, 8, 16...\}$ I realized you 
can get all even numbers between $n$ and $n+1$ by raising all possible subsets of 
$1$ to $n$ by two and summing them the individual subsets. Then the odd numbers 
can be found by adding $2^0$ to the set of even numbers, and since $2^0$ is not
in the set $\{ \mathbb{N}:2^n \}$ it does not break the rules of the question.  

```{r}
raise = function(x){
  sum(2^x) 
}

# first few natural numbers
n = 1:2
# produce the power set of n
sets = powerSet(n, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
evens = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
evens = unlist(evens)
odds = evens + 2^0
evens_and_odds = c(evens, odds)

sort(evens)
sort(odds)
sort(evens_and_odds)
```
We can similarly retrieve the odd numbers by including 0 in the set of $n$. In 
this case that would be `n = 0:2`. By including 0 in $n$, the carnality of 
$P(n)$ doubles because one more element is added to $n$, and the carnality 
of a power set is $|P(n)| = 2^{|n|}$. This is not much different from combining 
even numbers with the odd numbers as I did above (the set doubles in length). 

```{r}
# first few positive integers
z = 0:2
# produce the power set of z
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of z (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
Finally, if I go into the negatives and sum the "first" few values in 
$\mathbb{Z}$, this would be like adding fractions to the set of 
$\{n \in \mathbb{N}:2^n \}$. Like $\{z \in \mathbb{Z}:2^z \}$. I realized I 
start getting the set of real numbers, $\mathbb{R}$. 

```{r}
# first few natural numbers
z = -1:2
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
As we go more negative we achieve a higher "resolution". It seems like for each 
integer into the negative we go, one more decimal place is retrieved. For
$z \in Z$ where $-2 \le z \le1$ we get...

```{r}
# first few natural numbers
z = -2:1
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```

adding one more negative integer, $-3 \le z \le1$ we get...
```{r}
# first few natural numbers
z = -3:1
# produce the power set of n
sets = powerSet(z, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
nat_nums = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
nat_nums = unlist(nat_nums)
sort(nat_nums)
```
So then, is $\mathbb{R^+}$ the individual sums of the subsets of $P(\mathbb{Z})$ 
raised by 2? I did not complete a proof for power sets. If all this is true 
maybe it could be a fun way to get credit for writing a proof with power sets. 
Infinity gets involved though so maybe it is just false. 

Anyway, this is not what the question asked, but I spent too long thinking 
about it, so I have copied an answer from the internet for the sake of time. 

# ------------------------------------------------------------------------------
*Question 4.* 

**Rewrititng question.** 
for any $n \in \mathbb{N}$ we can write write it as $n = 2^{x_1}+2^{x_2}+...2^{x_i}$ 
where $x_0$ to $x_{i}$ are elements of the set $x \in P(\mathbb{N})$. 

(Base case) Showing 1 to 7 can be writen as $2^{x_1}+2^{x_2}+...2^{x_i}$. 
```{r}
raise = function(x){
  sum(2^x) 
}

# first few natural numbers
n = 0:2
# produce the power set of n
sets = powerSet(n, rev=TRUE)
# raise by 2 and sum each subset of n (in the powerset)
u = lapply(sets, raise)
# Just changing the data class to vector (from a list), and sriting them 
u = unlist(u)
sort(u)
```

Let $X$ be the set $\{x \in P(\mathbb{N});2^{x_1}+2^{x_2}+...2^{x_i} \}$.   
Suppose for the sake of argument that there is some $n \in \mathbb{N}$ where
$n \notin X$.  

Let $k$ be this number, and $t$ be the greatest factor of two that is less 
than $k$, and $\ell$ be the smallest factor of two greater than $k$. Such that
$t < k < \ell$ and $2t = \ell$.   

Then $k - t = m$ and $k = m + t$ where $m \in \mathbb{N}$, and $m < t < k$.
Since $m < t < k$ and $k$ is the smallest number not in $X$, it follows that 
$t,m \in X$.  

Similarly, because $t > m$, then $t + m \in X$. \
Note, if $m > t$ then $\ell$ would be the greatest factor of two that is less 
than $k$, not $t$.    
So $t + m = k$ and $t + m \in X$ but $k \notin X$. This is a contradiction.   
Therefore there all $n \in \mathbb{N}$ are in $X$.   




for any $n \in \mathbb{N}$ we can write write it as $n = 2^{x_1}+2^{x_2}+...2^{x_i}$ 
where $x_0$ to $x_{i}$ are elements of the set $x \in P(\mathbb{N})$.

Let the function $f(x)$ be $f(x) = 2^{x_1}+2^{x_2}+...2^{x_i}$. This is a binary 
function and preserves uniqueness. So that if $x_a \neq x_b$ where $x_a$ and  
$x_b$ $f(x_a)$












