---
output: pdf_document
---

### Homework 14: Functions
### author: "Jamie Ash"
### date: "2022-12-07"

**Question 1:** Let $f: X \rightarrow Y$ and $g: Y \rightarrow X$ both be functions. 
Determine whether each of the following statement is true or false. If a statement 
is true, prove it. Otherwise, provide a counter example. 

(a) if $g \circ f$ is injective, then $f$ is injective.

True.  
*Proof* Suppose $g \circ f$ is injective.   
So then by def. for any $a, a' \in X$, $g \circ f(a) \neq g \circ f(a')$ when 
$a \neq a'$. It follows that $g(f(a)) \neq g(f(a'))$ and $f(a) \neq f(a')$ 
(otherwise $g \circ f$ would not be injective).  
So then for any $a, a' \in X$, when $a \neq a'$ it follows that $f(a) \neq f(a')$.  
Therefore $f$ is injective.   


(b) if $g \circ f$ is injective, then $g$ is injective.  

False, $g$ can be surgective.   
Counter example...  
Let  $Y$ and $X$ be the sets $Y = \{a,b\}$ and $X = \{1, 2, 3\}$.   
Let $g$ and $f$ be the functions $g = \{ (1, a), (2, b), (3, b)\}$ 
and $f = \{(a, 1), (b, 2)\}$, so then $g \circ f = \{(a, a),(b, b)\}$.   
Here $g \circ f$ is injective, but $g$ is surgective.   
 
**Question 3:** Define $g: R \rightarrow R$ by $g(z) = 3z^2 - 4$. Find each of 
the following sets.

```{r}
# writing function of g(z) = 3z^2 - 4
g = function(z){
  3*z^2 - 4
} 

# Inverse function. Given the range will return the domain
gi = function(z){
  sqrt((z - 4)/3)
}
```

(c) $g([-2, 4])$  

*Answer:* I'm just inputting integers but the range is the same. So it's [8, 44].   
```{r}
g(-2:4)
```

(d) $g^{-1}((-10, 1))$ 

*Answer:* The function is undefined at this interval. A negative in the square root symbol
will return an imaginary number. So I'll go out on a limb and say $g^{-1}((-10, 1)) = \emptyset$.   

```{r, warning = FALSE}
gi(-10:1)
```

(e) $g(\emptyset)$  

*Answer:* Hmm... $\emptyset$?  

(f) $g^{-1}(\emptyset)$  

*Answer:* Hmm... $[-\inf, 4]$? or $- \inf < x < 4$ where $x$ is the input to the 
inverse relation.  

**Question 6:** Let $f: X \rightarrow Y$ be a function, and let $A,B \subset X$
and $C, D \subset Y$. Determine if each statement is true or false. If it's true
prove it, if it's false give a counterexample.  

*Note: It is not stated that $f$ is bijective, so while $f^{-1}$ is a 
relation, $f^{-1}$ may not be a function.

(k) $A \subset f^{-1}(f(A))$  

True.   
*Informal proof*
By def. $f^{-1}$'s range is a subset of the domain of $f$. Here the domain of 
$f$ is $A$, so then the range of $f^{-1}$ is a subset of $A$.   

(l) $f^{-1}(f(A)) \subset A$  

False. Let $f$ be surgective but not injective, so that $f^{-1}$ is not a 
function. This means the $f^{-1}(A)$ can map back to $A \cup B$ as long as 
$A \cap B$ are subsets of the domain of $f$, in this case $A \cap B \subset X$. 

(m) $C \subset f(f^{-1}(C))$  

True.
*Proof*

(m) $f(f^{-1}(C)) \subset C$  

True.
*Proof*





































