---
output: pdf_document
---

## Writting assignment 6

**name:** Jamie Ash  
**date:** 2022-09-22

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Tautology:** I will fly to Vietnam on Thursday, 2022-09-29, or I will not fly to Vietnam 
next on Thursday, 2022-09-29. 

This statement can be decomposed into two simpler statements.       
$P$: I will fly to Vietnam on Thursday, 2022-09-29.  
$Q$: I will not fly to Vietnam on Thursday, 2022-09-29.  

When $Q$ is not $\sim P$...  

```{r}
P = c(TRUE, FALSE) #true and false values for P 
Q = !P #not pee
PoQ = P|Q #pee or q
data.frame(P, Q, PoQ)
```

All possible outcomes of $P \cup Q$ are true, so my tautology is a tautology.   

$$\\[0.25in]$$

**Question 4:** If $4\nmid a^2$ the $a$ is odd.  

The contrapositive of question 4 is as follows...   

\begin{center}
If $a$ is even, then $4 \mid a^2$.  
\end{center}

*Proof:* Assume $a$ is even. So $a = 2k$ for $k \in Z$. It follows that 
$a^2 = 4(k)(k) = 4l$ for $l \in Z$. Thus the remainder of $4l/4$ is $l$ for 
$l \in Z$. This means $a^2/4 = l$ for $l \in Z$. Therefore $4 \mid a^2$.   

$$\\[0.25in]$$

**Question 6:** (For $x \in R$) If $x^2+5x < 0$, then $x<0$.   

The contrapositive of question 6 is as follows...   

\begin{center}
(For $x \in R$) If $x>0$, then $x^2 + 5x >0$.  
\end{center}

*Proof:* Assume $x>0$ and $x \in R$, then $x \in R^+$. Through the multiplicative 
property of $R^+$ we find $x^2+5x=y$, for $y \in R^+$. Therefore $x^2+5x>0$. 













































